### 2018-12-21 tex/paper.tex
Section on worst-case optimal submodular extension modified.

@@

\myparagraph{Worst-case Optimality}
In this paper, we focus on submodular extension families $\mathcal F(.)$ which
for each instance of the energy function $E(.)$ belonging to a given class $\mathcal E$ gives a corresponding
submodular extension ${\mathcal F}(E)$. Our extensions are derived from LP relaxations. When the LP relaxation is the tightest known, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This implies that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the extension is best for every instance of the energy function. 
Also, we seek a closed-form analytical expression for $\mathcal F$. For the sake of clarity,
in the analysis that follows we use $F$ to represent ${\mathcal F}(E)$ where
the meaning is clear from context.

\mysubsection{Pairwise Potts Model}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}:
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\mysubsection{Hierarchical Potts Model}
\label{sec:rhst_worst-case optimal}

@@

\mysubsection{Fast Conditional Gradient Computation for Dense CRFs}
\label{sec:dense_crf}

>>>>

In this paper, we focus on submodular extension families $\mathcal F(.)$ corresponding to different classes of energy functions $\mathcal E$. Given an instance of the energy function $E(.)$ from the class $\mathcal E$,  there is a corresponding submodular extension ${\mathcal F}(E)$. Also, we seek a closed-form analytical expression for $\mathcal F$.

@@

\myparagraph{Worst-case Optimality}

Our extensions are derived from LP relaxations. When the LP relaxation is the tightest known, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This implies that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the extension is best for every instance of the energy function. It may be possible to solve an optimisation problem to obtain the best extension for every given instace of energy $E(.)$. However, in this paper, we do not take that approach, and instead provide a general solution for a given class of energy function.

In subsection \ref{subsec:potts}, we prove the worst-case optimality of the submodular extension used in literature for the Potts model. In subsection \ref{subsec:hier_potts}, we obtain worst-case optimal submodular extension for the more general hierarchical Potts model. Finally, in subsection \ref{subsec:dense_crf}, we provide an approach to make our inference algorithm efficient for the dense CRF model. Using our approach, the inference algorithm has linear time-complexity in the number of variables and labels.

\mysubsection{Pairwise Potts Model}
\label{subsec:potts}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}:
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\mysubsection{Hierarchical Potts Model}
\label{subsec:hier_potts}

@@

\mysubsection{Fast Conditional Gradient Computation for Dense CRFs}
\label{subsec:dense_crf}
